---
title: 'Monitoring the spread of COVID-19 by estimating reproduction numbers over time'
output:
  html_document:
    theme: lumen
    self_contained: false
    lib_dir: html_libraries
---

Created by
[Prof. Dr. Thomas Hotz](https://www.tu-ilmenau.de/stochastik/team/thomas-hotz/),
[Stefan Heyder](https://www.tu-ilmenau.de/stochastik/team/stefan-heyder/),
[Matthias Glock](https://www.tu-ilmenau.de/stochastik/team/matthias-glock/)
and [Sebastian Semper](https://www.tu-ilmenau.de/stochastik/team/sebastian-semper/)
of the
[AG Stochastik](https://www.tu-ilmenau.de/stochastik/), [Technische Universität Ilmenau](https://www.tu-ilmenau.de/)
<br/>
in collaboration with
[Prof. Dr. Alexander Krämer](https://ekvv.uni-bielefeld.de/pers_publ/publ/PersonDetail.jsp?personId=21463&lang=de)
and
[Anne Böhle](mailto:anne.boehle@uni-bielefeld.de)
of the
[School of Public Health](https://www.uni-bielefeld.de/gesundhw/index.html), [Bielefeld University](https://www.uni-bielefeld.de/).

```{r libraries, echo = F, message = F, warning = F, results='hide'}
library(lubridate, warn.conflicts = F)
library(plotly, warn.conflicts = F)
Sys.setlocale('LC_TIME', 'C')
source("plot.r")
source("estimator.r")
```

```{r data, echo = F}
johns_hopkins <- read.csv("data/clean/data_world_jh.csv")
```

## {.tabset .tabset-fade .tabset-pills}

<!--
See https://github.com/rstudio/flexdashboard/issues/80#issuecomment-247139450
on generating tabs in rmarkdown automatically
-->
```{r, echo = F, warning = F, message = F}
df_num_days <- subset(johns_hopkins, select = c(reg0.name, tot.cases))
num_days <- aggregate(tot.cases ~ reg0.name, df_num_days, length)
countries <- unique(num_days$reg0.name[num_days$tot.cases > report.delay])

plots <- lapply(countries, function(country_name) {
    country <- johns_hopkins %>%
        filter(reg0.name == country_name) %>%
        mutate(date = ymd(date))

    estimates <- cbind(country, repronum(
            new.cases = country$new.cases,
            profile = infectivity,
            window = width,
            delay = report.delay,
            conf.level = 1 - alpha,
            pad.zeros = TRUE
        ))

    num.estimates <- sum(!is.na(estimates$repronum))
    if (num.estimates >= 3)  {
        plot_repronum(estimates, country_name, language = "en")
    }
    else {
        NA
    }
})

countries <- countries[!is.na(plots)]
plots <- plots[!is.na(plots)]

out <- lapply(seq_along(plots), function(i) {

  a1 <- knitr::knit_expand(text = sprintf("### %s\n", countries[i])) # tab header, auto extracts names of `hcs`
  a2 <- knitr::knit_expand(text = "\n```{r, echo = F, fig.width = 10, warning = FALSE}") # start r chunk
  a3 <- knitr::knit_expand(text = sprintf("\nplots[[%d]]", i)) # extract graphs by "writing" out `hcs[[1]]`, `hcs[[2]]` etc. to be rendered later
  a4 <- knitr::knit_expand(text = "\n```\n") # end r chunk

  paste(a1, a2, a3, a4, collapse = '\n') # collapse together all lines with newline separator
})
```

`r paste(knitr::knit(text = paste(out, collapse = '\n')))`

##

We show results for all countries with sufficiently many cases. Results for the world and for the 20 most affected countries can be found [here](index.html). In addition, results for Germany and its federal states (Bundesländer) based on official data are available [here](germany.html) (in German).

```{r echo=FALSE, results="asis"}
cat(paste(
    gsub("!NOW!", format(Sys.time(), '%d/%m/%y %H:%M', tz = "GMT"),
        readLines("notes.md")),
"\n"), sep = "\n")
```
