---
title: 'Monitoring the spread of COVID-19 by estimating reproduction numbers over time'
output:
  html_document:
    theme: lumen
    self_contained: false
    lib_dir: html_libraries
---

Created by
[Prof. Dr. Thomas Hotz](https://www.tu-ilmenau.de/stochastik/team/thomas-hotz/),
[Stefan Heyder](https://www.tu-ilmenau.de/stochastik/team/stefan-heyder/),
[Matthias Glock](https://www.tu-ilmenau.de/stochastik/team/matthias-glock/)
and [Sebastian Semper](https://www.tu-ilmenau.de/stochastik/team/sebastian-semper/)
of the
[AG Stochastik](https://www.tu-ilmenau.de/stochastik/), [Technische Universität Ilmenau](https://www.tu-ilmenau.de/)
<br/>
in collaboration with
[Prof. Dr. Alexander Krämer](https://ekvv.uni-bielefeld.de/pers_publ/publ/PersonDetail.jsp?personId=21463&lang=de)
and
[Anne Böhle](mailto:anne.boehle@uni-bielefeld.de)
of the
[School of Public Health](https://www.uni-bielefeld.de/gesundhw/index.html), [Bielefeld University](https://www.uni-bielefeld.de/).


```{r libraries, echo = F, message = F, warning = F, results='hide'}
library(lubridate, warn.conflicts = F)
library(plotly, warn.conflicts = F)
Sys.setlocale('LC_TIME', 'C')
source("plot.r")
source("estimator.r")

```

```{r data, echo = F}
johns_hopkins <- read.csv("data/clean/data_world_jh.csv")
world_tot <- read.csv("data/clean/data_world_tot.csv")
```

## {.tabset .tabset-fade .tabset-pills}

<!--
See https://github.com/rstudio/flexdashboard/issues/80#issuecomment-247139450
on generating tabs in rmarkdown automatically
-->
```{r, echo = F, warning = F, message = F}
numcountries <- 20

# add world tot. cases to johns-hopkins data
world_tot$reg0.name <- "World"
johns_hopkins <- merge(johns_hopkins, world_tot, all=TRUE)

maxday <- max(johns_hopkins$day)
df <- subset(johns_hopkins, day == maxday, select = c(reg0.name, tot.cases))
df <- df[rev(order(df$tot.cases)),]
countries <- unique(df$reg0.name[1:(numcountries + 1)])

plots <- lapply(countries, function(country_name) {
    country <- johns_hopkins %>%
        filter(reg0.name == country_name) %>%
        mutate(date = ymd(date))

    estimates <- cbind(country, repronum(
            new.cases = country$new.cases,
            profile = infectivity,
            window = width,
            delay = report.delay,
            conf.level = 1 - alpha,
            pad.zeros = TRUE
        ))

    plot_repronum(estimates, country_name, language = "en")
})

out <- lapply(seq_along(plots), function(i) {
  # tab header, auto extracts names of `hcs`
  a1 <- knitr::knit_expand(text = sprintf("### %s\n", countries[i]))

  # start r chunk
  a2 <- knitr::knit_expand(text = "\n```{r, echo = F, fig.width = 10, warning = FALSE}")

  # extract graphs by "writing" out `hcs[[1]]`,
  # `hcs[[2]]` etc. to be rendered later
  a3 <- knitr::knit_expand(text = sprintf("\nplots[[%d]]", i))

  # end r chunk
  a4 <- knitr::knit_expand(text = "\n```\n")

  # collapse together all lines with newline separator
  paste(a1, a2, a3, a4, collapse = '\n')
})

```

`r paste(knitr::knit(text = paste(out, collapse = '\n')))`

##

We show results for the world and for the `r numcountries` most affected countries  (by total number of infections). Results for all available countries can be found [here](all.html). Further results for Germany and its federal states (Bundesländer) based on official data are available [here](germany.html) (in German).

```{r echo=FALSE, results="asis"}
cat(paste(
    gsub("!NOW!", format(Sys.time(), '%d/%m/%y %H:%M', tz = "GMT"),
        readLines("notes.md")),
"\n"), sep = "\n")
```
